Detecting threats of violence in YouTube comments

### 2016-02-10 submission.tex
Added references

%todo: possibly a title that reflects the work better? 
\title{Detecting threats of violence in online discussions}

@@

\section{Introduction}
\label{sec:intro}
Threats of violence is an increasingly common occurrence in online
discussions. It disproportionally affects women and minorities, often
to the point of effectively eliminating them from taking part in
discussions online. Moderators of social networks operate on such a
big scale that manually reading all posts is an insurmountable
task. Methods for automatically detecting threats could therefore
potentially be very helpful, both to moderators of social networks,
and to the members of those networks.

In this article, we \ldots

@@

@@

The \ds consists of 9,845 comments, comprised of 28,643
sentences, see table \ref{tab:dataset}. In total there are 402,673 tokens in the sentences in the
data set. There are 1,285 comments containing threats, and 1,384
sentences containing threats, as seen in table \ref{tab:dataset}.
\cite{hammer2014} report inter annotator agreement on this data
set to be 98~\%, as calculated on 120 of the comments, doubly
annotated for evaluation.

Figure \ref{fig:comments} contains examples of some comments containing
\tovs{} taken from the data set. The first line is the username or
name, and the subsequent lines are the sentences of the comment. An
empty line indicates the end of a comment. The sentences are annotated
with a number indicating whether they contain a \tov{} (1), or not
(0).

LegitZombieSlayer1
0     As long as i'm alive you'll have no victory.
1     I'll kill all you cunts

@@

@@

\subsection{Experimental setup}

>>>>

%todo: possibly a title that reflects the work better? 
\title{Detecting threats of violence in YouTube comments}

@@

\section{Introduction}
\label{sec:intro}
Threats of violence is an increasingly common occurrence in online
discussions. It disproportionally affects women and minorities, often
to the point of effectively eliminating them from taking part in
discussions online. Moderators of social networks operate on such a
large scale that manually reading all posts is an insurmountable
task. Methods for automatically detecting threats could therefore
potentially be very helpful, both to moderators of social networks,
and to the members of those networks.

In this article, we evaluate different types of features for the task
of detecting threats of violence in YouTube comments. We show that ...

@@

\newcite{dinakar2011} proposes a method for the detection of
cyberbullying by targeting combinations of profane or negative words,
and words related to several predetermined sensitive topics. Their
data set consists of over 50,000 YouTube comments taken from videos
about controversial topics. The topics included sexuality, race,
culture and intelligence. The comments were grouped by topic, and then
12~\% of these were manually annotated to check that they were placed
in the right category.

The first stage of the detection was the same across all
categories. It consisted of using a lexicon of negative words and a
list of profane words, as well as part-of-speech tags from the
training data that were correlated with bullying. The second stage was
category-specific, and used commonly observed uni- and bigrams from
each category as features. The experiments reported accuracies from
63~\% to 80~\%, but did not report precision or recall.

@@

The data set consists of 9,845 comments, comprised of 28,643
sentences, see table \ref{tab:dataset}. In total there are 402,673
tokens in the sentences in the data set. There are 1,285 comments
containing threats, and 1,384 sentences containing threats, as seen in
table \ref{tab:dataset}.  \cite{hammer2014} report inter annotator
agreement on this data set to be 98~\%, as calculated on 120 of the
comments, doubly annotated for evaluation.

@@

%to-do: should we anonymize the user names?
Figure \ref{fig:comments} provides some examples of comments containing
\tovs{} taken from the data set. The first line is the username or
name, and the subsequent lines are the sentences of the comment. An
empty line indicates the end of a comment. The sentences are annotated
with a number indicating whether they contain a \tov{} (1), or not
(0).

@@

\subsection{Experimental setup}
%% todo:
%% - data split
%% - preprocessing
%% - machine learner
%% - tuning
%% - feature templates
